Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-06-30 Manuscript/manuscript.Rmd
edits

We first evaluated the least granular cell line specific random forest classifiers, that was one implemented using OC predictor types, without data re-sampling. We found that these models exhibited poor MCCs across all resolutions (Figure 4A (red)). We then assessing models built on OP predictor types, while still not performing any data resampling. Performances were similar to that of OC types, with no clear improvement (Figure 4B (red)). This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance.

@@

>>>>

We first evaluated the least granular cell line specific random forest classifiers, those were ones implemented using OC predictor types, without data re-sampling. We found that these models exhibited poor MCCs across all resolutions (Figure 4A (red)). We then assessing models built on OP predictor types, while still not performing any data resampling. Performances were similar to that of OC types, with no clear improvement (Figure 4B (red)). This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance.

@@

[Put this section last]
